\documentclass[line,letterpaper, 10pt]{res}
    \usepackage[none]{hyphenat}
    \usepackage{textcomp}
    \usepackage[utf8]{inputenc}
		\usepackage[T1]{fontenc}
		\pagestyle{empty}
\begin{document}
\name{{\LARGE Jorge P. Venegas Carrasco}}
\address{jorgepvenegas@gmail.com.com \ \ \textbullet \ \ \ San Francisco, CA \ \ \textbullet \ \ \ jorgepvenegas.com}
\begin{resume}
	% \vspace{-5mm}
	
	\section{Summary}
	Software Engineer, Front end, with 8+ years of experience in a broad spectrum of projects and technologies. As an agile culture enthusiast, I encourage collaboration between customers and teams making communication a strong pillar to rely on. I started as a back end engineer but my excitement for user interfaces and user satisfaction influenced my decision to get into front end engineering. I truly enjoy breaking down complex concepts into small, understandable knowledge pieces which can help to clarify interaction between coworkers with a different backgrounds and skill sets.

	\section{Working Experience}
	\textbf{Groupon}, {\sl Software Engineer, Frontend}\hfill August 2013 | Present\\\textbf{Data Science Platform} \hfill San Francisco, Bay Area
	\\
	\\Granular quality checking for data producers. Its purpose is to enforce clean data ingestion for data science pipelines.\\

	\begin{itemize} \itemsep 3pt
	\item Created web application which gives data producers a tool to create custom data quality measurement and alerts.
	\item Designed and implemented UI in React, Redux and API in Node with Express.
	\item Designed MySQL database to store data quality configurations.
	\end{itemize}

	\textbf{Platform Data Engineering}\\ \\Data mapping UI for Product Managers used to define rules and conditions given to our streaming platform. Users can test incoming sample data with a Translate feature which would run validations against rules previously defined, mitigating errors in the published data made available for other consumers in the company.\\
	\begin{itemize} \itemsep 3pt
	\item I led a complete application redesign and implementation from Backbone and Marionette to React and Redux.
	\item I was in charge of communications between users and backend team, addressing requests, feedback, and issues into new feature planification.
	\item I took leadership on UI and API development, which made me was the for users to solve issues and receive new requirements.
	\item Implemented Sandbox tool which allows users to play around with live data translations without affecting the production data pipeline. I designed metadata storage in MySQL and REST API in Java to support this feature.
	\end{itemize}

	\textbf{Taxonomy Service}\\ \\Web application built for Product Managers used to build taxonomies for product categorization, hierarchies and multiple language definitions.\\
	\begin{itemize} \itemsep 3pt
	\item I designed and implemented new UI in a single page application built in Ember.
	\item Improved UX by giving new tools like in-page update searching filters, in-place edition with rule validation, breadcrumb navigation and self-service .csv and .xls reports.
	\end{itemize}

	\textbf{Goods}\\ \\ Warehouse Management System for Groupon in Latin America.\\
	\begin{itemize} \itemsep 3pt
	\item I worked on several features for inventory management. Mostly I did HTML5, CSS3 and JavaScript with jQuery.
	\end{itemize}

	\textbf{Mobile Business}, {\sl Software Engineer}\hfill March 2012 | June 2013
	\\Santiago, Chile
	\\

	\begin{itemize} \itemsep 3pt
	\item Worked on RESTful API development in Java, used for web and mobile applications.
	\item Worked on GPS system mobile Android application for truck fleet.
	\item Implemented restaurant website catalog in HTML5, CSS3, jQuery and PHP.
	
	\end{itemize}

	\textbf{Stocker Group}, {\sl Web Developer}\hfill September 2010 | April 2011
	\\Santiago, Chile
	\\

	\begin{itemize} \itemsep 3pt
	\item Implemented designs created by the design team into HTML5, CSS3 and JavaScript.
	\item Encouraged the adoption of agile practices like stand up meetings, sprint planning and Kanban.
	\item Designed MySQL database for a tour management web application.
	
	\end{itemize}

	\section{Education}
	\textbf{Universidad de Ciencias de la Informática}\hfill 2011 | 2016
	\\{\sl BS in Computer Science} \hfill Santiago, Chile

	\section{Skills/Interests}
	\begin{itemize}
	\item JavaScript, Node, React, Redux, Ember, Webpack, UI/UX, HTML5, CSS3, SQL, Express, Git, TDD, Data Science, Java, REST, GraphQL, Vue, Agile, PHP.
	\item Bilingual, english and spanish (native).
	\item I volunteer as a mentor in NodeSchool San Francisco.
	\item Guitar, nonfiction reading and film photography are my favorite hobbies.
	\end{itemize}

\end{resume}
\end{document}